---
title: "project Final"
output: html_document
---



#**** Business Objective

# 1. Understand factors that affect car price
# 1.1 Identify variables that are significant in predicting the price of a car
# 1.2 How well do these variables predict the price of a car
```{r}
library(tidyverse)
library(DescTools)
```




```{r}
library(readr)
geely<-  read.csv("~/New folder/Geely_Dataset/CarPrice_Assignment.csv")
View(geely)
```

```{r}
attach(geely)
```

```{r}
summary(geely)
```
```{r}
?geely
```


// Variable description

The data-set contains the following Variables:


Car_ID	
Unique id of each observation (Interger)		

Symboling
Its assigned insurance risk rating, A value of +3 indicates that the auto is risky, -3 that it is probably pretty safe.(Categorical) 		

carCompany
Name of car company (Categorical)		

fueltype
Car fuel type i.e gas or diesel (Categorical)		

aspiration
Aspiration used in a car (Categorical)		

doornumber
Number of doors in a car (Categorical)		

carbody	
body of car (Categorical)		

drivewheel
type of drive wheel (Categorical)		

enginelocation	
Location of car engine (Categorical)		

wheelbase
Weelbase of car (Numeric)		

carlength
Length of car (Numeric)		

carwidth
Width of car (Numeric)		

carheight	
height of car (Numeric)		

curbweight
The weight of a car without occupants or baggage. (Numeric)		

enginetype
Type of engine. (Categorical)		

cylindernumber
cylinder placed in the car (Categorical)		

enginesize
Size of car (Numeric)		

fuelsystem
Fuel system of car (Categorical)		

boreratio	
Boreratio of car (Numeric)		

stroke
Stroke or volume inside the engine (Numeric)		

compressionratio
compression ratio of car (Numeric)		

horsepower
Horsepower (Numeric)		

peakrpm
car peak rpm (Numeric)		

citympg
Mileage in city (Numeric)		

highwaympg
Mileage on highway (Numeric)		

price(Dependent variable)		
Price of car (Numeric)


```{r}
library(Hmisc)
describe(geely)
```



```{r}
colSums(sapply(geely,is.na))
sum(is.na(geely))

length(which(is.na(geely)))
sapply(geely, function(x) length(which(x == "")))
sum(duplicated(geely))
```






```{r}
str(geely)
```

```{r}
dim(geely)
```

```{r}
names(geely)
```

```{r}
table(fueltype)
```

```{r}
table(aspiration)
```

```{r}
table(doornumber)
```

```{r}
table(carbody)
```

```{r}
table(drivewheel)
```

```{r}
table(enginelocation)
```

```{r}
table(enginetype)
```

```{r}
table(cylindernumber)
```

```{r}
table(fuelsystem)
```



```{r}
geely$cylindernumber[which(geely$cylindernumber=="four")] = 4
geely$cylindernumber[which(geely$cylindernumber=="six")] = 6
geely$cylindernumber[which(geely$cylindernumber=="five")] = 5
geely$cylindernumber[which(geely$cylindernumber=="eight")] = 8
geely$cylindernumber[which(geely$cylindernumber=="two")] = 2
geely$cylindernumber[which(geely$cylindernumber=="three")] = 3
geely$cylindernumber[which(geely$cylindernumber=="twelve")] = 12

```




```{r}
library(tidyverse)
library(tidyr)
geely=geely%>%separate(CarName,into=c("company_name","model"),sep=" ")
```



```{r}
geely$company_name=as.factor(geely$company_name)
```


```{r}
table(geely$company_name)
```



```{r}

geely<-geely%>%mutate(model = ifelse(is.na(model), "Not_available",geely$model))
```



```{r}
library(tidyverse)
attach(geely)
geely$company_name[which(geely$company_name=="toyouta")]="toyota"
geely$company_name[which(geely$company_name=="vokswagen")]="volkswagen"
geely$company_name[which(geely$company_name=="vw")]="volkswagen"
geely$company_name[which(geely$company_name=="Nissan")]="nissan"
geely$company_name[which(geely$company_name=="maxda")]="mazda"
geely$company_name[which(geely$company_name=="porcshce")]="porsche"
```


```{r}
table(geely$company_name)
```


```{r}

```


// convert the character variabls to factor 

```{r}
geely$fueltype       = as.factor(geely$fueltype)
geely$aspiration     = as.factor(geely$aspiration)
geely$doornumber     = as.factor(geely$doornumber)
geely$carbody        = as.factor(geely$carbody)
geely$drivewheel     = as.factor(geely$drivewheel)
geely$enginelocation = as.factor(geely$enginelocation)
geely$enginetype     = as.factor(geely$enginetype)
geely$cylindernumber = as.factor(geely$cylindernumber)
geely$fuelsystem     =  as.factor(geely$fuelsystem)
```

```{r}
geely$cylindernumber=as.integer(geely$cylindernumber)
```


```{r}
table(geely$doornumber) ### Need to change numbers
geely$doornumber = as.character(geely$doornumber)
geely$doornumber[which(geely$doornumber=="four")] = 4
geely$doornumber[which(geely$doornumber=="two")] = 2
geely$doornumber = as.integer(geely$doornumber)

```

```{r}
str(geely)
```



```{r}
geely_auto_Numeric = geely[,sapply(geely,is.numeric)]
dim(geely_auto_Numeric)
geely_auto_Category = geely[,sapply(geely,is.factor)]
dim(geely_auto_Category)
```


----------------------------------------------------------------------------------------------------

// Perform EDA

relationship bw 2  variables
```{r}
library(ggplot2)
```

// geom_boxplot
```{r}
ggplot(geely,mapping=aes(fueltype,price))+geom_boxplot()
```
// Line Chart

```{r}
ggplot(geely,mapping=aes(horsepower,price,col=geely$fueltype))+geom_line()
```

```{r}
ggplot(geely)+geom_histogram(mapping=aes(fill=enginetype,price),Position = "dodge")
```



```{r}
library(tidyverse)
```

```{r}
geely%>%filter(highwaympg>30)%>%ggplot(mapping=aes(horsepower,price,col=fueltype))+geom_line()+geom_point()
```

```{r}
geely%>%filter()%>%ggplot(mapping=aes(horsepower,price,col=drivewheel))+geom_line()+geom_point()
```



---------------------------------------------------------------------------------------------------------



## Model building




```{r}
r=sample(nrow(geely),nrow(geely)*0.9)
train=geely[r,]
test=geely[-r,]
```

```{r}

yup=lm(price~company_name,data =train)
summary(yup)
```
```{r}
str(model)
```

```{r}
geely$model=as.factor(geely$model)
```

```{r}
tr=predict(yup,test)
```

```{r}
mean((tr-test$price)^2)
```
##Tree 

```{r}
library(tree)

```


```{r}
tree_fit=tree(price~company_name,data=train)
tree_fit
```

```{r}
plot(tree_fit)
text(tree_fit,pretty=0)

```

```{r}
cv_gly=cv.tree(tree_fit)
cv_gly
```

```{r}
names(cv_gly)
```

```{r}
plot(cv_gly$size,cv_gly$dev,type = "b")
```


```{r}
prune_gly=prune.tree(tree_fit,best=3)
plot(prune_gly)
text(prune_gly,pretty=0)
```

```{r}
tr_predict=predict(tree_fit,newdata=test)
```



```{r}
plot(tr_predict,test$price)
abline(0,1)
mean((tr_predict-test$price)^2)
```





## Random Forest :


```{r}

library(randomForest)
```

```{r}
set.seed(1)
rfm=randomForest(train$price ~company_name,data=train)
summary(rfm)
```

```{r}
predict_rfm= predict(rfm, newdata=test)
```

```{r}
plot(predict_rfm,test$price)
abline (0,1)
mean((predict_rfm-test$price)^2)
```

